---
title: "p8130_HW1_brm2150"
author: "Brooklynn McNeil"
date: "2024-09-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

# Problem 1

Classify the following variables as qualitative (binary, nominal, or ordinal) or quantitative (discrete or continuous).

1.  Homework feedback, labeled as “poor”, “fair”, “good”, “very good”
    1.  **Qualitative - ordinal**
2.  Homework feedback, labeled as "fail", "pass"
    1.  **Qualitative - binary**
3.  Country of birth
    1.  **Qualitative - nominal**
4.  The quantity of grapes (in lbs) to make 3 liters of wine
    1.  **Quantitative - continuous**
5.  Number of TAs in the P8130 course
    1.  **Quantitative - discrete**

# Problem 2

```{r creating the dataframe, echo=FALSE}
dep_scr = c(45, 39, 25, 47, 49, 5, 70, 99, 74, 37, 99, 35, 8, 59)

summary(dep_scr)


```

1.  The mean is `r mean(dep_scr)`, the median is `r median(dep_scr)`, the range is `r range(dep_scr)`, and the standard deviation is `r sd(dep_scr)`.
2.  

```{r}
plot_df = tibble(
  ppl = c(1:14),
  dep_scr = c(45, 39, 25, 47, 49, 5, 70, 99, 74, 37, 99, 35, 8, 59)
)

ggplot(plot_df, aes(y = dep_scr)) +
  geom_boxplot()+
  labs(
    title = "BoxPlot of Depressions Scores from Bike Crash",
    y = "Depression Score"
  )

```

The Distribution of the data is right-skewed because the mean is greater than the median. The mode is 99.

# I DONT KNOW HOW TO FIND THE MODE YET

```{r}
bike_crash = c(45, 39, 25, 47, 49, 5, 70, 99, 74, 37, 99, 35, 8, 59)
car_crash = c(67, 50, 85, 43, 64, 35, 47, 97, 58, 58, 10, 56, 50)

plot_df = tibble(
  dep_scr = c(bike_crash,car_crash),
  crash_type = c(rep("bike", 14), rep("car", 13))
)

ggplot(plot_df) +
  geom_boxplot(
    aes(x = crash_type, y = dep_scr, fill = crash_type)
  ) +
  labs(
    title = "BoxPlot of Depressions Scores",
    y = "Depression Score"
  )
```

The bike crash data is right-skewed becauase the median is lower than the mean and the car crash data is left skewed slightly because the median is a little higher than the average

# Problem 3

1.   A = {2,4,6,8,10,12}
    1.  The probability of A is 6/12 or 1/2.
2.  B = {10}
    1.  the probability of 10 is 1/12.
3.   Compute P (B U A)

# Problem 4

P (women over 75 yrs have dementia) = 0.05

P (women over 75 with dementia have positive CT scan) = 0.80

P (women over 75 without dementia have positive CT scan) = 0.10

[Find the probability that a woman over 75 with a positive CT scan has dementia.]{.underline}
