---
title: "p8130_HW1_brm2150"
author: "Brooklynn McNeil"
date: "2024-09-17"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Problem 1

Classify the following variables as qualitative (binary, nominal, or ordinal) or quantitative (discrete or continuous).

1.  Homework feedback, labeled as “poor”, “fair”, “good”, “very good”
    1.  **Qualitative - ordinal**
2.  Homework feedback, labeled as "fail", "pass"
    1.  **Qualitative - binary**
3.  Country of birth
    1.  **Qualitative - nominal**
4.  The quantity of grapes (in lbs) to make 3 liters of wine
    1.  **Quantitative - continuous**
5.  Number of TAs in the P8130 course
    1.  **Quantitative - discrete**

## Problem 2

```{r creating the dataframe}
dep_scr = c(45, 39, 25, 47, 49, 5, 70, 99, 74, 37, 99, 35, 8, 59)

summary(dep_scr)


```

1. The mean is `r mean(dep_scr)`, the meadian is`r median(dep_scr)`, the range is `r range(dep_scr)`, and the standard deviation is `r sd(dep_scr)`.
2. 
```{r}
plot_df = tibble(
  ppl = c(1:14),
  dep_scr = c(45, 39, 25, 47, 49, 5, 70, 99, 74, 37, 99, 35, 8, 59)
)

ggplot(plot_df, aes(x = ppl, y = dep_scr)) +
  geom_boxplot()

```
